How to be a good member of a scientific software community [Article v\versionnumber]

### 2021-07-08 paper.tex
more text

@@

\begin{checklist}{Good community member}
\begin{itemize}
\item Tries to solve problem themselves first
\item Asks for help in the right place
\item Writes informative bug reports
\item Cites and acknowledges software appropriately
\item Contributes to the community
\item Treats fellow members and developers with courtesy and respect
\end{itemize}
\end{checklist}

>>>>

\subsection{Try to solve your own problem}

There's absolutely nothing wrong with needing help to figure out how to do
something with a new piece of software. Perhaps your use case wasn't considered
in the manual, or you're seeing behavior you don't expect. Perhaps you can't
even get it to install. Asking for help is very reasonable --- the developers
want people to use their software, and with that comes an implied obligation to
support those users. However, keep in mind that the developers of scientific
software are, for the most part, volunteering their time to provide that
support, and as such it's important to respect their time.

For this reason, asking the developers for help shouldn't be the \emph{first}
thing you do. Especially for software with a large community, chances are
someone else has run into similar difficulties, and you can probably save
yourself and the developers a lot of time if you look for solutions on your own
first. Indeed, quickly debugging your use of others' software is one of the
major skills one develops when learning to do computational research.

The first step is to check the manual. This might seem trivially obvious, but you'd be astonished how many emails developers get that are directly answered in the manual.

This might be an actual standalone
manual, or part of the web page for the software package, but if it exists it
should be your first stop. Look for a frequently asked questions list on the web site,

Search the internet for the error message (this works very well for software with thousands of users, less well with smaller packages)

@@

\begin{checklist}{Good community member}
\begin{itemize}
\item Tries to solve problem themselves first
\item Asks for help in the right place
\item Writes informative bug reports
\item Cites and acknowledges software appropriately
\item Treats fellow members and developers with courtesy and respect
\item Contributes to the community
\end{itemize}
\end{checklist}
